\section* {AII.3}
\label {a2-3}
\subsection*{(i)}

Suppose a $d$-hypergraph $G = (V,E)$ which every edge $e$ $\in$ $E$ incidenst to $d$ vertices in $V$. To formulate 0/1 linear programming, we introduce $X$ = \{ $x{_i}$, $x{_2}$, ... , $x{_n}$ \} which $x{_i}$ represents $v_i \in V$ in a linear programming.
If $x_i$ = 1, it means we pick $v_i$ to the set of double vertex cover, $C$ $\subset$ $V$, and otherwise $x_i$ = 0. For this solution, we want to find a minimum double vertex cover which requires at least 2 vertices from each edge are in $C$. Then, we can derive a constraint for 0/1 linear programming\\.

\begin{center}
$\sum\limits_{v_{i} \in e} x_i$ $\geq$ 2 for all $e \in E$ ;
\end{center}



Thus, we then formulate the linear programming.

\begin{tabbing}
	tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \kill \\ 
	\> \> Minimize \>\>\>\>\>$\sum\limits_{x=1}^n x_i$  \\ \\
	\> \> Subject to \\
	\> \> \> \> $\sum\limits_{v_{i} \in e} x_i$ $\geq$ 2 \> \> \> for all $e \in E$ ; at least 2 vertices are selected.\\
	\> \> \> \> $x_i$ = \{0,1\} \> \> \> for all $x_i \in X$ \\
\end{tabbing}

\subsection*{(ii)}

Because we can not solve 0/1 linear program in polynomial time, what we have to do next is to relax the program to be a normal
linear program by replacing \{0,1\} constraint with
$0 \leq x \leq 1$

Thus, the linear program is

\begin{tabbing}
  \label{relaxed_lp}
	tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \= tabs \kill \\ 
	\> \> Minimize \>\>\>\>\>$\sum\limits_{x=1}^n x_i$  \\ \\
	\> \> Subject to \\
	\> \> \> \> $\sum\limits_{v_{i} \in e} x_i$ $\geq$ 2 \> \> \> for all $e \in E$ ; at least 2 vertices are selected.\\
	\> \> \> \> $ 0 \leq x_i \leq 1 $ \> \> \> for all $x_i \in X$ \\
\end{tabbing}

Let $\tau$ denote the rounding threshold such that
\begin{align*}
    x_i = \begin{cases}
        1, & \text{if} x_i \geq \tau \\
        0, & \text{otherwise}
    \end{cases}
\end{align*}

\begin{algorithm}
  \caption{Finding double vertex cover}
  \label{alg:double_vertex_cover}
  \begin{algorithmic}
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \algnewcommand\algorithmicoperation{\textbf{Operation:}}
    \algnewcommand\Operation{\item[\algorithmicoperation]}
    \Require $V,E$
    \Ensure A minimum double vertex cover
    \Operation
    \State Solve the relaxed linear program corresponding to the given problem.
    \State \hspace{\algorithmicindent}  Minimize \hspace{\algorithmicindent} $\sum\limits_{x=1}^n x_i$
    \State \hspace{\algorithmicindent}  Subject to
    \State \hspace{\algorithmicindent}  \hspace{\algorithmicindent} $\sum\limits_{v_{i} \in e} x_i$ $\geq$ for all $e \in E$
    \State \hspace{\algorithmicindent}  \hspace{\algorithmicindent} $ 0 \leq x_i \leq 1 $ for all $x_i \in X$
    \State C $\leftarrow$ \{ $v_i \in V$ : $x_i \geq \tau$ \} \\
    \Return C
  \end{algorithmic}
\end{algorithm}

The next step is to derive $\tau$ such that all constraints are satisfied and the algorithm always return a valid solution. Let denote
$x^*$ to be an ideal value of any $x_i$ such that it satisfies all constraints.
\begin{align*}
\sum\limits_{v_{i} \in e} x_i &\geq 2 \\
\sum\limits_{i=1}^d x_i &\geq 2 \\
1 + \sum\limits_{i=1}^{d-1} x^i &\geq 2 \\
(d-1) x^i &\geq 1 \\
x_i &\geq \frac{1}{d-1} \\
\therefore \tau &= \frac{1}{d-1}
\end{align*}

Let denote $W$ denote the value of an optimal to the relaxed linear program and $OPT$ denote the minium number of double vertex cover.
Then $OPT \geq W$.

Now we can derive,
\begin{align*}
    |C| &= \sum\limits_{v_i \in C} 1 \\
        &\leq \sum\limits_{v_i \in C} (d-1)x_i \\
        &\leq (d-1) \sum\limits_{v_i \in C} x_i \\
        &\leq (d-1)W \\
        &\leq (d-1)OPT \\
\end{align*}

\subsection*{(iii)}
Lets take an example of a complete 3-hypergraph, where the optimal double vertex cover is $|V| - 1$ to make sure every edge has at least 2 vertices selected. So the result of the 0/1-LP is $|V| - 1$.

The relaxed-LP formulation is as follow:

\begin{itemize}
  \item Miminize $\sum_{i=1}^{n} x_i$
  
  \item Subject to:
    $\sum_{x_j \in e} x_j \geq 2$ for all edge $e$
    AND $0 \leq x_i \leq 1$
\end{itemize}

We run the algorithm by performing that relaxed-LP on the complete 3-hypergraph, and then round the result following the condition $x \geq \frac{1}{2}$.

For the complete 3-hypergraph, the relaxed-LP will return $x_i = \frac{2}{3}$ for all $i$ so that each sum of vertices in an edge is 2.

Then the algorithm will pick all of the vertices because they satisfy the condition. The result is:

\begin{align*}
  ALG = \frac{2}{3}|V|
\end{align*}

The integrality gap, denoted by $IG$, is:
\begin{align*}
  IG &= \frac{|V| - 1}{\frac{2|V|}{3}} \\
  &= \frac{3}{2} - \frac{3}{2|V|}
\end{align*}
