\section* {AII.2}
\label {a2-2}
\subsection*{(i)}

The best case of the solution is when there is a common variable in every clause, then the optimal solution is that variable. Thus:

$$ OPT \ge 1 = LB $$

In this problem, we are not to sure whether the duplication of variables in a DNF clause is allowed or not. If it is allowed, we can define a CNF like this:

$$(a \vee b \vee c) \wedge (a \vee b \vee b) \wedge (a \vee a \vee a) $$

In the worst case, the algorithm picks $c, b, a$ sequentially. So $ALG = 3 = n$. Thus the approximation ratio is $\frac{n}{LB} = n$.

This result is not very interesting because $n$ is also the upper bound of the solution. Indeed, $(a \vee a)$ can be reduced to only $a$, thus the clause is not in the 3-CNF form anymore.

Assume that such duplication is not allowed. Then in the worst case, $OPT = 1$ as we explained before, while the algorithm can pick at most $n-2$ variables. It is because if all of $n$ variables are used, then the last 2 ones are in some DNF claus(es) which are covered by the previous variables. If not all of them are used, then $ALG < n-2$. \\

The case when $ALG = n - 2$ is as follow, we have $n$ variables and 2 common ones in all clauses.
$$ (x_1 \vee x_2  \vee x_3) \wedge (x_1 \vee x_2 \vee x_4) \wedge (x_1 \vee x_2 \vee x_5) \wedge ... \wedge (x_1 \vee x_2 \vee x_n) $$
There are 2 common variables and $n-2$ other different variables distributed among the clauses. In the worst case, the algorithm returns $ALG = n-2 $. Then the approximation ratio is

$$\rho = \frac{n-2}{OPT} = n-2$$

\subsection*{(ii)}
For the algorithm to become a 3-approximation algorithm it should be modified so that in each iteration it chooses all three elements in a clause and eliminate all the clauses in CNF that contain any of these three elements.\\

\textbf{Proof}

Let $ D^* $ be a subset of $ D $ that only contains clauses that do not share any variable.

The optimal solution to the problem $ OPT $ contains at least one variable from each clause in $D^*$ therefore :
$$ OPT \ge |D^*|$$ 

In our algorithm after the modification, we select three variables in each clause in $ D^* $,
because there are no clauses that share common variables with them.
The other clauses which have common variables as any clause in $ D^* $ are deleted.
Thus:
\begin{align*}
	ALG &= 3 |D^*| \\
	&\leq 3 OPT
\end{align*}

Therefore it is a 3-approximation algorithm.
